Compiling refinement types to dependent types

### 2020-07-20 tex/paper.tex
Properly define context mapping

\paragraph{Contexts.}
We start with defining $\tranctx$,
which is the simplest translation of the three.
It merely maps the types of the bindings in a (well-formed) context
from the surface language into the core language.

\begin{equation}
\begin{aligned}
  & \tranctx(\emptyset)
      && \triangleq
    \emptyset                                               \\
  & \tranctx(\nonterm G, \gterm x : \nonterm{ts})
      && \triangleq
    \tranctx(\nonterm G), \gterm x : \tranty(\nonterm {G} \vdash \nonterm{ts})  \\
\end{aligned}
\end{equation}

>>>>

\paragraph{Contexts.}
As a warm-up,
we start with defining $\Tranctx$,
which is the simplest translation of the three.
It merely maps the types of the bindings in a (well-formed) context
from the surface language into the core language.

\begin{itemize}
  \item \ranchor{TCTX-Empty}.
    \begin{align*}
      & \inferrule{~}
                  {\emptyset \text{~ok}}
          \longmapsto
        \emptyset.
    \end{align*}
    The base case is trivial: we map the empty context to the empty context.
  \item \ranchor{TCTX-Bind}.
    \begin{align*}
      & \inferrule{\nonterm G \text{~ok} \\ \nonterm G \vdash \nonterm{ts}}
                  {\nonterm G , \gterm x : \nonterm{ts} \text{~ok}}
          \longmapsto
        \Tranctx(\nonterm G \text{~ok}), x : \tranty(\nonterm G \vdash \nonterm{ts}).
    \end{align*}

    We recurse on the prefix $\nonterm G$,
    which we are allowed to do due to the $\nonterm G \text{~ok}$ premise,
    and we use $\tranty$ to get the translated type of $\gterm x$,
    which we are also allowed to do due to the corresponding premise.
\end{itemize}
